Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-19 paper.tex
Change contents for the theoretical part

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in Eq. \ref{eq:2D-Moss-perp}. Here
we choose the thickness of as 2D material as its ``covalent''
thickness $\delta_{\mathrm{cov}}$, which is
defined as the longest distance along the z-direction between any two
atom nuclei plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
  + r_{i}^{\mathrm{cov}} + r_{j}^{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r^{\mathrm{cov}}_{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
Figure \ref{fig-3}b, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$ indeed
shows an excellent linear correlation with $\delta_{\mathrm{cov}}$,
with $R^{2}=0.98$, and the slope very close to $1/4\pi$. In addition
to our theoretical predictions discussed above, the perfect linear
correlation between $\alpha^{\perp}$ and $\delta_{\mathrm{cov}}$ has
its strong physical meaning. Similar to the molecular polarizability
which characterizes the volume of electron cloud of an isolated
molecule \cite{Israelachvili_2011}, the 2D polarizability also
characterizes the volume of the electron cloud of a 2D material per
unit area (from its definition), and naturally represents the
thickness of the electron cloud of the 2D material. The fact that the
thickness of the electron cloud of a 2D material can be approximated
by the extension of valence states in the z-direction, explains the
close match between the linear slope in Figure \ref{fig-3}c and
$1/4\pi$. In other wordst, the universal scaling relation for
$\alpha^{\perp}$ indicates the quantity
$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
thickness of a 2D material. We propose that the well-established
experimental protocol for measuring the electronic polarizability of
isolated molecules \cite{Antoine_1999}, can also be extended to
measure $\alpha^{\perp}$ of a 2D material, as a direct estimation of
it thickness, in comparison with the optical ellipsometry techniques
\cite{Weber_2010} widely used to estimate the thickness of 2D
materials, which requires empirical optical model and parameter
fitting.

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently-published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
overlap them with our results in Figure \ref{fig-3}b and \ref{fig3-c}
(further details see Supplementary Section S3). Althought the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals, apparent linear trends can be observed for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$, with the linear coefficient
very close to the HSE06 results. Therefore, the proposed universal 2D
Moss-like relations are confirmed.  We have also tested the potential
relation between the 2D polarizabilities with other physical
quantities, including the effective carrier mass, quantum capacitance
and total atomic polarizabilities, while no apparent correlations are
found (details see Supplementary Section S3).

In short, we have revealed the 2D analog of the Moss relation for both
polarization direction by using the 2D polarizability: $\alpha^{\parallel}$ is inversely proportional
to the minimal bandgap $E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the
characteristic thickness of the 2D material.

\iffalse
\subsection{Theoretical Explanations}
\label{sec:theory}

Similar to the treatment of quantum wells (QW), the wavefunction of an
isolated 2D material $\psi(\mathbf{r})$ can be separated into the in-
and out-of-plane components \cite{davies_physics_1997}
$\psi^{\parallel}(\mathbf{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\mathbf{\rho}=(x, y)$ is
the in-plane coordinate. According to the Bloch theorem, the periodic
in-plane wavefunction can be further expressed as
$\psi^{\parallel}(\mathbf{\rho})=e^{ik\rho}u(\rho)$, where $k$ is the
in-plane wave vector and $u(\rho)$ is periodic function in the
xy-plane. According to the random phase approximation theory
\cite{Adler_1962}, $\varepsilon_{\mathrm{SL}}$ can be calculated by
taking the $\mathbf{q} \to 0$ and $\omega \to 0$ limits of the
non-interacting dielectric function $\varepsilon(\mathbf{q}, \omega)$,
where $\mathbf{q}$ is the momentum transfer and $\omega$ is the
frequency:
\begin{equation}
  \label{eq:RPA-eps2}
  \varepsilon_{\mathrm{SL}}
  = \varepsilon_{\mathrm{SL}}(\mathbf{q} \to 0)
  = 1 + \frac{2e^{2}}{\varepsilon_{0} |q|^{2} \Omega}
  \sum_{\mathrm{k, c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
  \left[f(\psi_{\mathrm{c}}) - f(\psi_{\mathrm{v}}))\right]
\end{equation}
where $e$ is the unit charge, c, v are the conduction and valence
bands, $f$ is the Fermi-Dirac distribution, $E$ is the eigenenergy of
individual bands, and $f$ is the Fermi-Dirac distribution. Taking the
limit that $L\to\infty$, when
$\varepsilon^{\perp}_{\mathrm{SL}} \approx 1$, we have
$1-1/\varepsilon^{\perp}_{\mathrm{SL}} \approx
(\varepsilon_{\mathrm{SL}}^{\perp} - 1)$. Therefore $\alpha^{\parallel}$ and $\alpha^{\perp}$ at 0 K can be unified by the same equation:
\begin{equation}
  \label{eq:alpha-RPA}
  \alpha = \frac{2e^{2}}{|q|^{2}A} \sum_{\mathrm{k,c,v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|e^{-i\mathbf{q}\mathbf{r}}|\psi_{\mathrm{c}}(\mathbf{k+q})>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k+q}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the direction is determined by $\mathbf{q}$. For
$\alpha^{\parallel}$, $e^{-i\mathbf{qr}}$ is independent of
$z$. Further combining with the Bloch wave representation and the k-p
theory\cite{Jiang_2017_Eg_Eb}, we have:
\begin{equation}
  \label{eq:alpha_para_RPA}
  \alpha^{\parallel} = \frac{2e^{2}}
  {(2 \pi)^{2}} \int d^{2}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
the final expression for Eq. \ref{eq:alpha_para_RPA} is shown to be
$\alpha^{\parallel} = N e^{2}/(2\pi E_{\mathrm{g}})$ by
Ref. \citenum{Jiang_2017_Eg_Eb}, where $N$ is degeneracy of bands
associated with the minimal bandgap. This explains the linear
correlation we observe between $1/\alpha^{\parallel}$ and
$E_{\mathrm{g}}$. When $\alpha^{\parallel}$ is measured in
$(4 \pi \varepsilon_{0})\cdot \mathrm{\AA}$ and $E_{\mathrm{g}}$
measured in eV, the linear regression slope in Figure \ref{fig-3}b is
predicted to be
$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$. The
observed value of $\sim$0.166 corresponds to $N$ between 2 and 3,
which is reasonable for the 2D materials studied.

On the other hand, the $E_{\mathrm{g}}$ independence and correlation
with the covalent thickness of $\alpha^{\perp}$, can also be explained
using the same quantum framework. Generally speaking, $\psi^{\perp}$
follows the Hamiltonian in z-direction, such that:
\begin{equation}
  \label{eq:Hamil-z}
  \left[-\frac{\hbar^{2}}{2 m^{\perp}}\nabla^{2} + V(z)\right] \psi^{\perp}(z) = E \psi^{\perp}
\end{equation}
where $\hbar$ is the reduced Planck constant and $m^{\perp}$ is the
effective mass in the perpendicular direction. $V(z)$ is the potential
created by the 2D material, and confined within a region of length
$\delta$. For simplicity we use plane wave to model the in-plane
wavefunction, that
$\psi^{\parallel}(\mathbf{\rho}) \propto
e^{i\mathbf{k\rho}}$. Inserting into Eq. \ref{eq:alpha-RPA} and
perform the Taylor expansion of $e^{-i\mathbf{qr}}$, we can eliminate
the contribution from the in-plane
wavefunctions\cite{davies_physics_1997} and get:
\begin{equation}
  \label{eq:alpha_perp_RPA}
  \alpha^{\perp} = \frac{2e^{2}}{(2 \pi) ^{2}} \int d^{2}\mathbf{k}
  \sum_{\mathrm{c, v}}
  \frac{|<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k}>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
where the integration over $\mathbf{k}$ is done in the $k_{x}-k_{y}$
part of the Brillouin Zone. In a confined 1D system, the matrix
element
$<\psi_{\mathrm{v}}(\mathbf{k})|z|\psi_{\mathrm{c}}(\mathbf{k})>$ is
usually proportional to the length of confinement $\delta$, while the
eigenenergy difference $E_{\mathrm{c}}-E_{\mathrm{v}}$ is correlated
with $\delta^{-2}$, while independent of
$\mathbf{k}$\cite{Benedict_1995}. Therefore the integrated
$\alpha^{\perp}$ is also independent of the bandgap $E_{\mathrm{g}}$,
which would instead greatly influence $\alpha^{\parallel}$. Using a
simplified particle-in-box model, we evaluated the integration of
Eq. \ref{eq:alpha_perp_RPA} and show that $\alpha^{\parallel}$ is
related with the geometric parameter $\delta$ (details see Supplementary Section SXX \todo{add note}), the confinement of
electrons in the z-direction, which nicely explains our finding of
correlation between $\alpha^{\perp}$ and
$\delta^{\mathrm{cov}}_{\mathrm{2D}}$.

Based on unit analysis of the 2D polarizability, its in- and
out-of-plane components can be described as the characteristic
lengthes in both directions. In fact, such characteristic length is
just the dielectric screening length. The potential from a point
charge inside the 2D material generates an in-plane potential
$V(\rho)$ as function of distance $\rho$ from the point charge, in the
Keldysh form \cite{Keldysh_1979_eps_multi,Pulci_2014}:
\begin{equation}
  \label{eq:Keldysh}
  V(\rho) = \frac{e}{4 \alpha^{\parallel}}
  \left[H_{0}(\frac{2\varepsilon_{0}\rho}{\alpha^{\parallel}})
    - Y_{0}(2 \varepsilon_{0}\frac{\rho}{\alpha^{\parallel}})\right]
\end{equation}
The length $r^{\parallel}_{0} = \alpha^{\parallel}/(2\varepsilon_{0})$
determines the degree of in-plane dielectric screening: the charges
feel strong screening when $\rho/r^{\parallel}_{0} \ll 1$ while the
screening for $\rho/r^{\parallel}_{0} \gg 1$ reduces to the case of
vacuum. In other words, the quantity
$\alpha^{\parallel}/(2\varepsilon_{0})$ characterizes the radius of
localized in-plane screened potential. Combining with the result that
the thickness of 2D material is characterized by
$\alpha^{\perp}/\varepsilon_{0}$, we have drawn a generalized picture
of the dielectric nature of 2D materials via the 2D polarizability:
the dielectric screening of a point charge sitting in the middle of a
2D material can be viewed as an ellipsoid with the length of
principle axes to be $\alpha^{\parallel}/(2 \varepsilon_{0})$ and
$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively. Beyond the
boundary the ellipsoid the dielectric screening gradually reduced to
the vacuum situation. Note such radius is not essentially the 2D
exciton radius, which is still related with the effective mass
\cite{Chernikov_2014_EB_MoS2_2D3D}. Nevertheless, with the universal
relation between $\alpha^{\parallel}-E_{\mathrm{g}}$ and
$\alpha^{\perp}-\delta_{\mathrm{2D}}^{\mathrm{cov}}$ for 2D materials,
we are able to quantitatively predict and design the dielectric nature
of a new 2D material by engineering the bandgap and geometry, which
can greatly enhance our understanding and application of 2D materials.

\fi

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
\caption{\label{fig-delta} Scheme for the determination of the
  covalent thickness of one-atom-thick (left) and few-atom-thick
  (right) 2D materials.}
\end{figure}

>>>>

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in Eq. \ref{eq:2D-Moss-perp}. Here
we choose the thickness of as 2D material as its ``covalent''
thickness $\delta_{\mathrm{cov}}$, which is
defined as the longest distance along the z-direction between any two
atom nuclei plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z_{i} - z_{j}|
  + r_{i}^{\mathrm{cov}} + r_{j}^{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r^{\mathrm{cov}}_{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c). As shown in
Figure \ref{fig-3}b, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$ indeed
shows an excellent linear correlation with $\delta_{\mathrm{cov}}$,
with $R^{2}=0.98$, and the slope very close to $1/4\pi$. In addition
to our theoretical predictions discussed above, the perfect linear
correlation between $\alpha^{\perp}$ and $\delta_{\mathrm{cov}}$ has
its strong physical meaning. Similar to the molecular polarizability
which characterizes the volume of electron cloud of an isolated
molecule \cite{Israelachvili_2011}, the 2D polarizability also
characterizes the volume of the electron cloud of a 2D material per
unit area (from its definition), and naturally represents the
thickness of the electron cloud of the 2D material. The fact that the
thickness of the electron cloud of a 2D material can be approximated
by the extension of valence states in the z-direction, explains the
close match between the linear slope in Figure \ref{fig-3}c and
$1/4\pi$. In other wordst, the universal scaling relation for
$\alpha^{\perp}$ indicates the quantity
$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
thickness of a 2D material. We propose that the experimental
measurment of the electronic polarizability
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, can also be
extended to measure $\alpha^{\perp}$ of a 2D material, as a direct
estimation of it thickness, in comparison with the optical
ellipsometry techniques \cite{Weber_2010} widely used to estimate the
thickness of 2D materials, which requires empirical optical model and
parameter fitting.

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently-published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
overlap them with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(further details see Supplementary Section S3). Althought the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals, apparent linear trends can be observed for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$, with the linear coefficient
very close to the HSE06 results. Therefore, the proposed universal 2D
Moss-like relations are confirmed.  We have also tested the potential
relation between the 2D polarizabilities with other physical
quantities, including the effective carrier mass, quantum capacitance
and total atomic polarizabilities, while no apparent correlations are
found (details see Supplementary Section S3).

In short, we have revealed the 2D analog of the Moss relation for both
polarization direction by using the 2D polarizability:
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the characteristic
thickness of the 2D material. Although their apparent forms in
Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} seem different, we
will show the 2D Moss-like relations stem from the same origin. In
merit of the unit analysis, $\alpha^{\parallel}$ and $\alpha^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. Specifically,
$\alpha^{\parallel}$ and $\alpha^{\perp}$ corresponds to
characteristic lengthes in- and out-of-plane, respectively. The
in-plane screened electrostatic potential $V(r)$ from a point charge
in an 2D plane, as a function of distance $r$,
\cite{Keldysh_1979_eps_multi,Pulci_2014}:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$, where $H_{0}$
is the Struve function and $Y_{0}$ is the Bessel function of second
kind, is assciated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
$V(r,r/r^{\parallel}_{0} \gg 1)$ reduces to the simple Coulombic
potential in vacuum. Combining with the result that the thickness of
2D material is characterized by $\alpha^{\perp}/\varepsilon_{0}$, we
have drawn a generalized picture of the dielectric nature of 2D
materials via the 2D polarizability: the dielectric screening of a
point charge sitting in the middle of a 2D material can be viewed as
an ellipsoid with the length of principle axes to be
$\alpha^{\parallel}/(2 \varepsilon_{0})$ and
$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively, analog to the
polarizability ellipsoid picture of molecules used in spectroscopy
\cite{Banwell_1994}. The in-plane screening length is generally larger
for a smaller bandgap semiconductor, which qualitatively explains the
inverse propotional relation between $\alpha^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

@@

% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
% \caption{\label{fig-delta} Scheme for the determination of the
  % covalent thickness of one-atom-thick (left) and few-atom-thick
  % (right) 2D materials.}
% \end{figure}
